Compiling refinement types to dependent types

### 2020-07-19 tex/paper.tex
Add a conjecture that units don't break λC
No need for `ok` in `Γ |- τ ok`

\begin{figure}[ht]
  \footnotesize
  \drules[TWF]{$\nonterm G \vdash \nonterm{ts} \text{ ok}$}{type well-formedness}{TrueRef,Base,Conj,Arr}
  \drules[T]{$\nonterm G \vdash \nonterm{es} : \nonterm{ts}$}{term typing}{Unit,Var,Abs,App,Case,Con,Sub}
  \caption{Surface language typing}
  \label{fig:surface_typing}
\end{figure}

@@

We take $\lambda C$ \cite{TTFPLambdaC}
with a unit type as our core dependently typed language.

>>>>

\begin{figure}[ht]
  \footnotesize
  \drules[TWF]{$\nonterm G \vdash \nonterm{ts}$}{type well-formedness}{TrueRef,Base,Conj,Arr}
  \drules[T]{$\nonterm G \vdash \nonterm{es} : \nonterm{ts}$}{term typing}{Unit,Var,Abs,App,Case,Con,Sub}
  \caption{Surface language typing}
  \label{fig:surface_typing}
\end{figure}

@@

We take $\lambda C$ \cite{TTFPLambdaC}
with a unit type as our core dependently typed language.
We conjecture that the introduction of units
does not break the usual metatheoretical properties of the system.
